Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-05 src/paper.tex
update

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{bm}

@@

@@

\begin{center}
\begin{tabular}{ c c c }
    \hline
    cell1 & cell2 & cell3 \\ 
    \hline
    cell4 & cell5 & cell6 \\  
    cell7 & cell8 & cell9    
\end{tabular}
\end{center}

>>>>

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{bm}
\usepackage{multirow}
\usepackage{tabularx, colortbl, makecell}

@@

\begin{table}
    % \setlength{\tabcolsep}{12pt} % Adjust column spacing
    % \renewcommand{\arraystretch}{1.3}
    \begin{center}
        \begin{tabular}{llllll}
            System                & type & size & DNSMOS & dWER   & Sim  \\
            Mixture               & -          & -          & 2.68   & 79.3\% & -        \\
            Target & -          & -          & 3.32   & 11.3\% & 0.653    \\
                                  &            &            &        &        &          \\
            Spex+                 & Continuous & 11M        & 2.98   & 19.3\% & 0.923    \\
            Continuous     & Continuous & 220M       & 3.27   & 14.7\% & 0.877    \\
            TSELM       & Hybrid     & 468M       & 3.22   & 19.8\% & 0.924\_d \\
                                  &            &            &        &        &          \\
            TSELM-S               & Discrete   & 354M       & 3.24   & 28.1\% & 0.892\_d \\
            TSELM-M               & Discrete   & 389M       & 3.22   & 28.4\% & 0.901\_d \\
            TSELM-L               & Discrete   & 468M       & 3.22   & 27.1\% & 0.905\_d
            \end{tabular}
      \end{center}
      \caption{This table }
  \end{table}

\subsection{Baseline models}

TSELM is compared with

@@

% % \begin{center}
% \begin{table*}{ c c c c c c c c }
%     \hline
%     System & Type & Model size & DNSMOS & dWER & Spk Sim 
% \end{table*}
% % \end{center}

% \begin{table*}[t]
%     \centering
%     \begin{tabular}{lcr}
%         \hline
%       \multirow{2}{System} & 2 & 3 \\
%       4 & 5 & 6 \\
%       7 & 8 & 9
%     \end{tabular}
%     \caption{Blabla}
%     \label{tab:1}
%   \end{table*}
